---
title: "Statistical Analysis Report"
subtitle: "Analysis Summary Template"
author: "Ed Harris"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: right
    number-sections: true
    code-fold: show
    code-tools: true
    theme: lux
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
editor: visual
execute:
  echo: true
  warning: false
  message: false
---

# Summary

Provide a brief overview of the analysis objectives, key findings, and main conclusions. This section should be concise and accessible to non-technical stakeholders. Max 1 paragraph, no bullet points

# Introduction

Briefly describe the context and motivation for the analysis. What problem are you trying to solve or what question are you trying to answer?  List the main objectives of the analysis. Max 1 paragraph, no bullet points.

# Data

Describe where the data comes from, how it was collected, and any relevant details about data provenance. Max 1 paragraph (usually a few sentences unless the experimental design is described in detail), no bullet points.

```{r setup}
#| label: setup
#| include: false

# Load required packages
library(tidyverse)
library(knitr)

# Set global options
knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  fig.align = "center"
)

# Helper function for better table formatting
format_table <- function(df, caption = NULL) {
  knitr::kable(df, caption = caption, format = "simple", digits = 3)
}
```

```{r data}
#| label: data
#| echo: true

# Load your data
# data <- read.csv("your_data.csv")

# For demonstration, using built-in dataset
data <- mtcars

# Display structure of the data
str(data)

# Display first few rows
head(data) %>%
  kable(caption = "Dataset sample")
```

# Statistical Analysis

Describe the statistical methods and techniques used in this analysis. Max 1 paragraph (usually a few sentences), no bullet points.

# Results

Present the results of the analysis in a clear and concise manner. Usually there should be a brief summary of each statistical test with an appropriate accompanying graph or table.  For a multivariate model with multiple predictors, present the results in a table with the predictor names and the corresponding p-values, accompanied by a graph of the relationship between each predictor and the response variable.

# References

List any references or citations used in the analysis.

# Appendix {.appendix}

**Session Information**

```{r session-info}
#| label: session-info

sessionInfo()
```

