---
title: "Statistical Analysis Report"
subtitle: "Analysis Summary Template"
author: "Ed Harris"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    code-fold: show
    code-tools: true
    theme: cosmo
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
editor: visual
execute:
  echo: true
  warning: false
  message: false
---

# Executive Summary

Provide a brief overview of the analysis objectives, key findings, and main conclusions. This section should be concise and accessible to non-technical stakeholders.

**Key Findings:**

-   Finding 1
-   Finding 2
-   Finding 3

# Introduction

## Background

Describe the context and motivation for the analysis. What problem are you trying to solve or what question are you trying to answer?

## Objectives

Clearly state the objectives of this analysis:

1.  Objective 1
2.  Objective 2
3.  Objective 3

## Research Questions

-   Research question 1?
-   Research question 2?

# Data

## Data Source

Describe where the data comes from, how it was collected, and any relevant details about data provenance.

## Data Description

```{r setup}
#| label: setup
#| include: false

# Load required packages
library(tidyverse)
library(knitr)
library(kableExtra)

# Set global options
knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  fig.align = "center"
)
```

```{r load-data}
#| label: load-data
#| echo: true

# Load your data
# data <- read.csv("your_data.csv")

# For demonstration, using built-in dataset
data <- mtcars
```

### Data Structure

```{r data-structure}
#| label: data-structure

# Display structure of the data
str(data)
```

### Summary Statistics

```{r summary-stats}
#| label: summary-stats

# Summary statistics
summary(data)
```

### Sample of Data

```{r data-sample}
#| label: data-sample

# Display first few rows
head(data) %>%
  kable(caption = "Sample of the dataset") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Data Quality Assessment

### Missing Values

```{r missing-values}
#| label: missing-values

# Check for missing values
missing_summary <- data %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Missing_Count")

missing_summary %>%
  kable(caption = "Missing values by variable") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Data Cleaning Steps

Describe any data cleaning, transformation, or preprocessing steps:

1.  Step 1: Description
2.  Step 2: Description

```{r data-cleaning}
#| label: data-cleaning

# Example data cleaning
# data_clean <- data %>%
#   filter(!is.na(variable)) %>%
#   mutate(new_variable = transformation)
```

# Exploratory Data Analysis

## Univariate Analysis

### Numerical Variables

```{r univariate-numerical}
#| label: univariate-numerical
#| fig-cap: "Distribution of numerical variables"

# Example: Histogram
data %>%
  ggplot(aes(x = mpg)) +
  geom_histogram(bins = 20, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Miles per Gallon",
       x = "MPG",
       y = "Frequency") +
  theme_minimal()
```

### Categorical Variables

```{r univariate-categorical}
#| label: univariate-categorical
#| fig-cap: "Distribution of categorical variables"

# Example: Bar plot
data %>%
  ggplot(aes(x = factor(cyl))) +
  geom_bar(fill = "coral") +
  labs(title = "Distribution of Cylinders",
       x = "Number of Cylinders",
       y = "Count") +
  theme_minimal()
```

## Bivariate Analysis

### Relationships Between Variables

```{r bivariate-analysis}
#| label: bivariate-analysis
#| fig-cap: "Relationship between variables"

# Example: Scatter plot
data %>%
  ggplot(aes(x = wt, y = mpg)) +
  geom_point(size = 3, alpha = 0.6, color = "darkblue") +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  labs(title = "Relationship between Weight and MPG",
       x = "Weight (1000 lbs)",
       y = "Miles per Gallon") +
  theme_minimal()
```

### Correlation Analysis

```{r correlation}
#| label: correlation
#| fig-cap: "Correlation matrix"

# Correlation matrix
cor_matrix <- cor(data[, sapply(data, is.numeric)])

# Display correlation table
cor_matrix %>%
  kable(digits = 3, caption = "Correlation matrix") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Statistical Methods

## Methodology

Describe the statistical methods and techniques used in this analysis:

-   Method 1: Description and justification
-   Method 2: Description and justification

## Assumptions

List and verify any assumptions required for the statistical methods:

1.  Assumption 1
2.  Assumption 2

### Checking Assumptions

```{r check-assumptions}
#| label: check-assumptions
#| fig-cap: "Diagnostic plots"

# Example: Check normality
# qqnorm(data$variable)
# qqline(data$variable)
```

# Results

## Primary Analysis

### Model Fitting

```{r model-fitting}
#| label: model-fitting

# Example: Linear regression
model <- lm(mpg ~ wt + hp + cyl, data = data)

# Model summary
summary(model)
```

### Model Diagnostics

```{r model-diagnostics}
#| label: model-diagnostics
#| fig-cap: "Model diagnostic plots"
#| fig-width: 10
#| fig-height: 8

# Diagnostic plots
par(mfrow = c(2, 2))
plot(model)
```

### Results Summary

```{r results-table}
#| label: results-table

# Extract model coefficients
coef_table <- broom::tidy(model, conf.int = TRUE)

coef_table %>%
  kable(digits = 3, caption = "Model coefficients with 95% confidence intervals") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Interpretation

Interpret the results in context:

-   **Variable 1**: Interpretation
-   **Variable 2**: Interpretation

## Secondary Analyses

### Additional Tests

```{r additional-tests}
#| label: additional-tests

# Additional statistical tests
# Example: ANOVA
# anova_result <- aov(mpg ~ factor(cyl), data = data)
# summary(anova_result)
```

### Subgroup Analysis

If applicable, present any subgroup analyses:

```{r subgroup-analysis}
#| label: subgroup-analysis
#| fig-cap: "Results by subgroup"

# Example: Analysis by subgroup
# data %>%
#   group_by(subgroup) %>%
#   summarise(mean_outcome = mean(outcome),
#             sd_outcome = sd(outcome))
```

## Effect Sizes and Practical Significance

Discuss the practical significance of findings, not just statistical significance:

```{r effect-sizes}
#| label: effect-sizes

# Calculate effect sizes
# Example: R-squared
r_squared <- summary(model)$r.squared
adj_r_squared <- summary(model)$adj.r.squared

cat("R-squared:", round(r_squared, 3), "\n")
cat("Adjusted R-squared:", round(adj_r_squared, 3), "\n")
```

# Discussion

## Key Findings

Summarize the main findings from the analysis:

1.  Finding 1 with interpretation
2.  Finding 2 with interpretation
3.  Finding 3 with interpretation

## Limitations

Discuss any limitations of the analysis:

-   Limitation 1
-   Limitation 2
-   Limitation 3

## Implications

What are the practical implications of these findings?

## Future Directions

Suggest areas for future research or analysis:

-   Direction 1
-   Direction 2

# Conclusions

Provide clear, concise conclusions based on the analysis. Address the original research questions and objectives.

# References

List any references or citations used in the analysis.

# Appendix {.appendix}

## Session Information

```{r session-info}
#| label: session-info

sessionInfo()
```

## Additional Tables and Figures

Include any supplementary materials here.

```{r additional-analysis}
#| label: additional-analysis
#| eval: false

# Additional code or analyses
```

