---
title: "Statistical Analysis Report"
subtitle: "Analysis Summary Template"
author: "Ed Harris"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: right
    number-sections: true
    code-fold: show
    code-tools: true
    theme: lux
    embed-resources: true
  pdf:
    toc: false
    number-sections: true
    colorlinks: true
editor: visual
execute:
  echo: true
  warning: false
  message: false
---

# Summary

Provide a brief overview of the analysis objectives, key findings, and main conclusions. This section should be concise and accessible to non-technical stakeholders. Max 1 paragraph, no bullet points

# Introduction

This analysis is to demonstrate the use of Artificial Intelligence (AI) Large Language Models (LLMs)to analyse data. The goal here is to stress test LLMs on a simple analysis task that involves a linear mixed effects model with a binary dependent variable and a blocking factor. The report will be in the form of a statistical analysis report.

# Data

The data are from a subset of the Chz2006 dataset in the R package {agricolae} (Mendiburu and Yaseen 2020). There are 3 factors of interest(crop, amendment, and block) and a binary dependent variable (wilt_percent). There is also a plant individual factor which we will not consider here. There are n = 1920 observations in the data. The data experimentally meassures the incidence and performance of healthy tubers and rotten potato field infested with naturally Ralstonia solanacearum Race 3/Bv 2A, after application of inorganic amendments and a rotation crop in Carhuaz Peru, 2006.

```{r setup}
#| label: setup
#| include: false

# Load required packages
library(tidyverse)
library(knitr)
library(lme4) # Statistician's preference
library(lmerTest) # Calculates your p-vals in case CI is not good enough for you
library(sjPlot)

# Set global options
knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  fig.align = "center"
)

# Helper function for better table formatting
format_table <- function(df, caption = NULL) {
  knitr::kable(df, caption = caption, format = "simple", digits = 3)
}
```

```{r data}
#| label: data
#| echo: false

# Load your data
wilt <- read.csv("wilt.csv")

# convert to factor
wilt$block <- factor(wilt$block)

# This here creates a binary version of the wilt var
wilt$wilt_bin <- wilt$wilt_percent
wilt$wilt_bin[wilt$wilt_bin == 50] <- 1

# Display structure of the data
str(wilt)

# Display first few rows
head(wilt) %>%
  kable(caption = "Dataset sample")
```

# Statistical Analysis

The statistical analysis consisted of a linear mixed effects model with a binary dependent variable and a blocking factor treating block as a random effect. The model was fitted using the lme4 package in R.

# Results

The results of the analysis are presented below with the predictor names and the corresponding p-values, accompanied by a graph of the relationship between each predictor and the response variable.

```{r analysis}
#| label: analysis
#| echo: false

lme1 <- glmer(wilt_bin ~ crop + amendment + (1|block), 
            data = wilt,
            family = binomial(link = "logit") )

# print(lme1, corr=F)

print("Model Summary")
summary(lme1, corr=F)

plot_model(lme1, type = "pred", terms = c("crop"))

plot_model(lme1, type = "pred", terms = c("amendment"))

```


# References

Mendiburu, Felipe de and Yaseen, Muhammad(2020).  agricolae:
  Statistical Procedures for Agricultural Research.R package version 1.4.0, https://myaseen208.github.io/agricolae/https://cran.r-project.org/package=agricolae.

# Appendix {.appendix}

**Session Information**

```{r session-info}
#| label: session-info

sessionInfo()
```