---
title: "Statistical Analysis Report"
subtitle: "Analysis Summary Template"
author: "Ed Harris"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: right
    number-sections: true
    code-fold: show
    code-tools: true
    theme: lux
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
editor: visual
execute:
  echo: true
  warning: false
  message: false
---

# Summary

Provide a brief overview of the analysis objectives, key findings, and main conclusions. This section should be concise and accessible to non-technical stakeholders. Max 1 paragraph, no bullet points

# Introduction

This analysis is to demonstrate the use of Artificial Intelligence (AI) Large Language Models (LLMs)to analyse data. The goal here is to stress test LLMs on a simple analysis task that involves a linear mixed effects model with a binary dependent variable and a blocking factor. The report will be in the form of a statistical analysis report.

# Data

The data are from a subset of the CIC dataset in the R package {agricolae} (Mendiburu and Yaseen 2020). There are 3 factors of interest(crop, amendment, and block) and a binary dependent variable (wilt_percent). There is also a plant individual factor which we will not consider here. There are n = 1920 observations in the data.

```{r setup}
#| label: setup
#| include: false

# Load required packages
library(tidyverse)
library(knitr)

# Set global options
knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  fig.align = "center"
)

# Helper function for better table formatting
format_table <- function(df, caption = NULL) {
  knitr::kable(df, caption = caption, format = "simple", digits = 3)
}
```

```{r data}
#| label: data
#| echo: true

# Load your data
# data <- read.csv("wilt.csv")

# For demonstration, using built-in dataset
data <- mtcars

# Display structure of the data
str(data)

# Display first few rows
head(data) %>%
  kable(caption = "Dataset sample")
```

# Statistical Analysis

Describe the statistical methods and techniques used in this analysis. Max 1 paragraph (usually a few sentences), no bullet points.

# Results

Present the results of the analysis in a clear and concise manner. Usually there should be a brief summary of each statistical test with an appropriate accompanying graph or table. For a multivariate model with multiple predictors, present the results in a table with the predictor names and the corresponding p-values, accompanied by a graph of the relationship between each predictor and the response variable.

# References

List any references or citations used in the analysis.

# Appendix {.appendix}

**Session Information**

```{r session-info}
#| label: session-info

sessionInfo()
```